Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-28 reanalysis-4-outcome_analysis.qmd
refactor

# Display key variables
key_vars <- c("ever_lapse_binary", "dr_severityNPDR", "dr_severityPDR", "any_treatment")
key_results <- full_results[full_results$Variable %in% key_vars, ]

>>>>

# Display key variables
key_vars <- c("ever_lapse_binary", "dr_severityNPDR", "dr_severityPDR")
key_results <- full_results[full_results$Variable %in% key_vars, ]
